HPC--101\\Onboarding

### 2016-05-11 hpc_101/paper.tex
switched to latex elipsis
updates to the text on several slides.  Offset commands during testing of user accounts to show commands in blue

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Template Heavily modified by David Schanzenbach
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{etoolbox}
\usepackage{lmodern}% http://ctan.org/pkg/lm
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{anyfontsize}
\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{calc}
\usepackage{makecell}
\usepackage{xstring}
\mode<presentation> {

@@

\subsection{{\craycs}}
\begin{frame}
\frametitle{{\craycs} -- History}
\begin{itemize}
 \item Initial investment of 1.8 Million by the University of {\hawaii} (UH)
 \item Delivered in October of 2014
 \item Accepted in December of 2014 
 \item Early adopter testing started in January 2015
 \item Opened for general use in April 2015
 \item March 2016, 92 new nodes added to cluster, raising total core count to 5,876 cores
 \item As of March 2016, more than 240 users have been granted access to the cluster
\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{{\craycs} -- Storage}
	Two storage options are currently available on the {\craycs}
	\begin{enumerate}
		\item {\lustre}
		\item ValueStorage
	\end{enumerate}
\end{frame}

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ {\lustre}}
	\begin{itemize}
		\item {\lustre} is a high performance parallel filesystem
		\item The {\craycs} has $\approx582$TB of storage space
		\item Shared between all compute nodes and login nodes
		\item Primarily used as scratch space for jobs (Input and Output)
		\item User do not have a usage quota (soft or hard)
		\item Certain directories are subject to a 90 day purge policy
		\item \textbf{Data is not backed up!  Users are responsible for their own data}
                \item {\lustre} utilizes RAID 6 arrays, and is fairly robust but \ldots~\\RAID is not a backup
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ ValueStorage}
	\begin{itemize}
		\item $500$TB of scale out storage
		\item Is only available for purchase by cluster users~\\and only accessible via the login nodes
		\item Purchased in 0.5TB increments
	\end{itemize}
	\btVFill

	\begin{center}
	\textbf{ValueStorage Pricing}~\\ 
		\resizebox{0.75\textwidth}{!}{%
		\begin{tabular}{l r ||l r }
			\toprule
			\textbf{Product} & \textbf{Annual Cost}~~ & ~~\textbf{Product} & \textbf{Annual Cost}\\
	\midrule
			\midrule
			0.5TB & \$65.00~~ & ~~0.5TB + Replication  & \$130.00 \\
			\bottomrule
		\end{tabular}
		}
		~\\ \href{http://www.hawaii.edu/its/value-storage-pricing/}{More Information}
		~\\	{\footnotesize \emph{All prices are subject to change}}
	\end{center}
\end{frame}

@@

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, exclusive.q, lm.q, gpu.q, sb.q, kill.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

\subsection{Connecting to a cluster @ UH}
\begin{frame}
	\frametitle{Connecting to a cluster @ UH}
	\begin{description}[\setlength{\leftmargini}{0pt}]
	\item[] \begin{itemize}
		\item To connect to the cluster, we utilize a client which communicates using the Secure Shell (\emph{SSH}) protocol 
		\item Linux and MacOSX, typically have a SSH client already installed
		\item Windows typically does not come with an SSH client installed
		\item Windows 10 may come pre-installed with a SSH client, but it might not be stable
		\item Suggested SSH clients for Windows include:
		\begin{itemize}
			\item \href{http://www.hawaii.edu/askus/685}{SSH Secure Shell}~(SSH 3.2.9)
			\item \href{http://www.chiark.greenend.org.uk/~sgtatham/putty/download.html}{Putty}
                        \item \href{http://mobaxterm.mobatek.net/}{MobaXterm}
		\end{itemize}
	\end{itemize}
	\item[] ~\\
	\item[] \begin{itemize}
		\item The {\craycs} has two login nodes:
		\begin{itemize}
			\item uhhpc1.its.hawaii.edu
			\item uhhpc2.its.hawaii.edu
		\end{itemize}
	\end{itemize}
	\end{description}
	{\large Let's attempt to login!}
\end{frame}

@@

\begin{frame}
\frametitle{On Initial Login~\ldots}
	Validate that all system permissions are correct for your user~\\
	\begin{enumerate}
		\item Test that you can list files in your home: `\texttt{ls -la}'    
		\item Test making a file in your home: `\texttt{touch test.txt}'    
		\item Go into \ctilde{}/lus: `\texttt{cd \ctilde{}/lus/}'  
		\item Test making a file in your lus directory: `\texttt{touch test.txt}'   
		\item Go into \ctilde{}/apps:  `\texttt{cd \ctilde{}/apps/}'     
		\item Test making a file in your apps directory: `\texttt{touch test.txt}'   
	\end{enumerate}
	\begin{alertblock}{Result}
		\begin{center}Did you get any errors?  Let us know if you did\end{center}
	\end{alertblock}
	\btVFill

@@

\section{Problem Reporting}
\begin{frame}
\frametitle{Problem Reporting}
\begin{itemize}
\item Always email UH-HPC-Help@lists.hawaii.edu
\item For batch jobs...
\begin{itemize}
\item[--] Job ID, path to submission script, submission command, error file location, output files
\end{itemize} 
\item For other problems...
\begin{itemize}
\item[--] State the problem, command issued, host, directory, remote host, error messages
\end{itemize}
\end{itemize}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Template Heavily modified by David Schanzenbach
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{etoolbox}
\usepackage{lmodern}% http://ctan.org/pkg/lm
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{anyfontsize}
\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{calc}
\usepackage{makecell}
\usepackage{xstring}
\usepackage{color}
\mode<presentation> {

@@

\subsection{{\craycs}}
\begin{frame}
\frametitle{{\craycs} -- History}
\begin{itemize}
 \item Initial investment of 1.8 Million by the University of {\hawaii} (UH)
 \item Delivered in October of 2014
 \item Accepted in December of 2014 
 \item Early adopter testing started in January 2015
 \item Opened for general use in April 2015
 \item March 2016, 92 new nodes added to cluster, raising total core count from 3,800 to 5,876 cores
 \item As of March 2016, more than 257 users have been granted access to the cluster
\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{{\craycs} -- Storage}
	Two storage options are currently available on the {\craycs}
	\begin{enumerate}
		\item {\lustre}
                  \begin{itemize}
                  \item High performance parallel filesystem 
                  \item Available on all the cluster nodes
                    \item Freely available to all users
                  \end{itemize}
		\item ValueStorage
                  \begin{itemize}
                  \item Network attached scale out storage
                  \item Only available from the login nodes
                  \item Available as a for fee service
                  \end{itemize}
	\end{enumerate}
\end{frame}

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ {\lustre}}
	\begin{itemize}
		\item The {\craycs} has $\approx582$TB of storage space

		\item Primarily used as scratch space for jobs (Input and Output)
		\item User do not have a usage quota (soft or hard)
		\item Certain directories are subject to a 90 day purge policy
		\item \textbf{Data is not backed up!  Users are responsible for their own data}
                \item {\lustre} utilizes RAID 6 arrays, and is fairly robust but \ldots~\\RAID is not a backup
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ ValueStorage}
        ~\\
	\begin{itemize}
		\item $500$TB of scale out storage
		\item Purchased annually in 0.5TB increments 
	\end{itemize}
	\btVFill

	\begin{center}
	\textbf{ValueStorage Pricing}~\\ 
		\resizebox{0.50\textwidth}{!}{%
		\begin{tabular}{l r }
			\toprule
			\textbf{Product} & \textbf{Annual Cost}~~ \\
	                \midrule
			\midrule
			0.5TB & \$65.00\\
                        0.5TB + Replication  & \$130.00 \\
			\bottomrule
		\end{tabular}
		}
		~\\ \href{http://www.hawaii.edu/its/value-storage-pricing/}{More Information}
		~\\	{\footnotesize \emph{All prices are subject to change}}
	\end{center}
\end{frame}

@@

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for free to all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, exclusive.q, lm.q, gpu.q, sb.q, kill.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

\subsection{Connecting to a cluster @ UH}
\begin{frame}
	\frametitle{Connecting to a cluster @ UH}
	\begin{description}[\setlength{\leftmargini}{0pt}]
	\item[] \begin{itemize}
		\item To connect to the cluster, an SSH client is required
		\item Linux and MacOS X, typically have a SSH client already installed
		\item Windows typically needs a 3rd party SSH client
		\item Suggested SSH clients for Windows include:
		\begin{itemize}
			\item \href{http://www.hawaii.edu/askus/685}{SSH Secure Shell}~(SSH 3.2.9)
			\item \href{http://www.chiark.greenend.org.uk/~sgtatham/putty/download.html}{Putty}
                        \item \href{http://mobaxterm.mobatek.net/}{MobaXterm}
		\end{itemize}
	\end{itemize}
	\item[] ~\\
	\item[] \begin{itemize}
		\item The {\craycs} has two login nodes:
		\begin{itemize}
			\item uhhpc1.its.hawaii.edu
			\item uhhpc2.its.hawaii.edu
		\end{itemize}
	\end{itemize}
	\end{description}
        ~\\~\\
	{\large Let's attempt to login!}
\end{frame}

@@

\begin{frame}
\frametitle{On Initial Login~\ldots}
	Validate that all system permissions are correct for your user~\\
	\begin{enumerate}
		\item Test that you can list files in your home: `\textcolor{blue}{\texttt{ls -la}}'    
		\item Test making a file in your home: `\textcolor{blue}{\texttt{touch test.txt}}'    
		\item Go into \ctilde{}/lus: `\textcolor{blue}{\texttt{cd \ctilde{}/lus/}}'  
		\item Test making a file in your lus directory: `\textcolor{blue}{\texttt{touch test.txt}}'   
		\item Go into \ctilde{}/apps:  `\textcolor{blue}{\texttt{cd \ctilde{}/apps/}}'     
		\item Test making a file in your apps directory: `\textcolor{blue}{\texttt{touch test.txt}}'   
	\end{enumerate}
	\begin{alertblock}{Result}
		\begin{center}Did you get any errors?  Let us know if you did\end{center}
	\end{alertblock}
	\btVFill

@@

\section{Problem Reporting}
\begin{frame}
\frametitle{Problem Reporting}
\begin{itemize}
\item Always email UH-HPC-Help@lists.hawaii.edu
\item For batch jobs \ldots
\begin{itemize}
\item[--] Job ID, path to submission script, submission command, error file location, output files
\end{itemize} 
\item For other problems \ldots
\begin{itemize}
\item[--] State the problem, command issued, host, directory, remote host, error messages
\end{itemize}
\end{itemize}
\end{frame}
